A fully labelled proof system for intuitionistic modal logics

### 2020-09-15 FullyLabelled/JLC/introduction.tex
footnote

\todo{Add Bozin and Dozen reference: \cite{bovzic1984models} and Maffezioli and Naibo \cite{maffezioli2014}}
\lutz{I've added a refence to \cite{bovzic1984models} in sec.2. But \cite{maffezioli2014} is totally unrelated, and I don't see the point in citing that}\todo{cite them when we indroduce F1 and F2, because they have something similar}
%\todo{maybe paragraph on related work?}

>>>>

\todo{Add Bozin and Dozen reference: \cite{bovzic1984models} and Maffezioli and Naibo \cite{maffezioli2014}}
\lutz{I've added a refence to \cite{bovzic1984models} in sec.2, and \cite{maffezioli2014} in a footnote in sec.3}
%\todo{maybe paragraph on related work?}

### 2020-09-15 FullyLabelled/JLC/system.tex
footnote

Finally, in the semantics, the two relations $\rel$ and $\le$ are
strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$. These need to be reflected at the level of the proof system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.
%
However, these two rules create new labels, and in order to be
complete, the system needs the \emph{monotonicity} rule $\llabrn{mon}$, shown on the left below. 
\begin{equation}
  \label{eq:mono}
  \vlinf{\llabrn{mon}}{}{\lseq{\B, \futs{x}{y}}{\Left, \labels{x}{A}}\Right}{
    \lseq{\B, \futs{x}{y}}{\Left, \labels{x}{A}, \labels{y}{A}}\Right}
  \hskip6em
  \vlinf{\rlabrn{mon}}{}{\lseq{\B, \futs{x}{y}}{\Left}{\Right, \labels{y}{A}}}{
    \lseq{\B, \futs{x}{y}}{\Left}{\Right, \labels{x}{A}, \labels{y}{A}}}
\end{equation}
Since this rule is a form of contraction, it would cause the same
problems as contraction in a cut elimination proof. Hence, it is
preferable to have a system in which this rule is admissible. This is
the reason why we have monotonicity incorporated in the rules
$\rn{id}$, $\llabrn\IMP$ and $\llabrn\BOX$ in Figure~\ref{fig:labIKp},
instead of using the rules in~\eqref{eq:nomon}. Then, not only
$\llabrn{mon}$ but also its right-hand side version $\rlabrn{mon}$,
shown on the right in~\eqref{eq:mono} above become admissible.

>>>>

Finally, in the semantics, the two relations $\rel$ and $\le$ are
strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$. These need to be reflected at the level of the proof system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.\footnote{The logic studied in~\cite{maffezioli2014} has similar semantic conditions (two binary relations in a Kripke frame) that lead to similar rules as ours in the proof system.}
%
However, these two rules create new labels, and in order to be
complete, the system needs the \emph{monotonicity} rule $\llabrn{mon}$, shown on the left below. 
\begin{equation}
  \label{eq:mono}
  \vlinf{\llabrn{mon}}{}{\lseq{\B, \futs{x}{y}}{\Left, \labels{x}{A}}\Right}{
    \lseq{\B, \futs{x}{y}}{\Left, \labels{x}{A}, \labels{y}{A}}\Right}
  \hskip6em
  \vlinf{\rlabrn{mon}}{}{\lseq{\B, \futs{x}{y}}{\Left}{\Right, \labels{y}{A}}}{
    \lseq{\B, \futs{x}{y}}{\Left}{\Right, \labels{x}{A}, \labels{y}{A}}}
\end{equation}
Since this rule is a form of contraction, it would cause the same
problems as contraction in a cut elimination proof. Hence, it is
preferable to have a system in which this rule is admissible. This is
the reason why we have monotonicity incorporated in the rules
$\rn{id}$, $\llabrn\IMP$ and $\llabrn\BOX$ in Figure~\ref{fig:labIKp},
instead of using the rules in~\eqref{eq:nomon}. Then, not only
$\llabrn{mon}$ but also its right-hand side version $\rlabrn{mon}$,
shown on the right in~\eqref{eq:mono} above become admissible.
